Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-12-03 Docs/IJES/journal.tex
New Final version: abstract word count problem solved

\begin{abstract}
We present new alternative approaches to solve the hardware and software (HW-SW) partitioning problem. First, we use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem. In a nutshell, the multi-core SMT-based BMC approach allows initializing many verification instances using different approaches based on the number of available processing cores. In particular, each instance checks for a different optimum value until the optimization problem is satisfied. We implement our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC). Additionally, we integrate the maximum satisfiability solver $\nu$Z tool into ESBMC, which provides a portfolio of approaches for solving linear optimization problems over SMT formulas. We compare all proposed approaches to a state-of-the-art optimization tool (MATLAB). Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks, but ESBMC-$\nu$Z outperforms all parallel approaches proposed in this paper.
\end{abstract}

>>>>

\begin{abstract}
We present new alternative approaches to solve the hardware and software (HW-SW) partitioning problem. First, we use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing to create four variants to solve the partitioning problem. Multi-core SMT-based BMC approach allows initializing many verification instances using different approaches based on the number of available processing cores. In particular, each instance checks for a different optimum value until the optimization problem is satisfied. We implement our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC). Additionally, we integrate the maximum satisfiability solver $\nu$Z tool into ESBMC, which provides a portfolio of approaches for solving linear optimization problems over SMT formulas. We compare all proposed approaches to a state-of-the-art optimization tool (MATLAB). Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks.
\end{abstract}
